Reionization Planck 2018 Notes

### 2021-01-07 results/notes.tex

>>>>

\begin{figure}
%
\includegraphics[width=0.35\textwidth]{cosmomc_kde/pl18_tanh_highz_test5_run1_vs_relike_tanh_highz_test9_run1_f0p28_taulo_prior_0p03_zre_prior_6p1_taulo_prior_0p0_tri.png}
\includegraphics[width=0.35\textwidth]{results/cosmomc_kde/pl18_tanh_highz_test5_run1_vs_relike_tanh_highz_test9_run1_f0p28_taulo_prior_0p03_zre_prior_6p1_taulo_prior_0p0_tri_smooth_scale_1D_2_num_bins_1D_20_smooth_scale_2D_2_num_bins_2D_25.png}
%
\includegraphics[width=0.35\textwidth]{cosmomc_kde/pl18_tanh_highz_test5_run1_vs_relike_tanh_highz_test9_run4_f0p18_taulo_prior_0p03_zre_prior_6p1_taulo_prior_0p0_tri.png}
\includegraphics[width=0.35\textwidth]{cosmomc_kde/pl18_tanh_highz_test5_run1_vs_relike_tanh_highz_test9_run4_f0p18_taulo_prior_0p03_zre_prior_6p1_taulo_prior_0p0_tri_smooth_scale_1D_2_num_bins_1D_20_smooth_scale_2D_2_num_bins_2D_25.png}
%
\includegraphics[width=0.35\textwidth]{cosmomc_kde/pl18_tanh_highz_test5_run1_vs_relike_tanh_highz_test8_run9_f0p14_taulo_prior_0p03_zre_prior_6p1_taulo_prior_0p0_tri.png}
\includegraphics[width=0.35\textwidth]{cosmomc_kde/pl18_tanh_highz_test5_run1_vs_relike_tanh_highz_test8_run9_f0p14_taulo_prior_0p03_zre_prior_6p1_taulo_prior_0p0_tri_smooth_scale_1D_2_num_bins_1D_20_smooth_scale_2D_2_num_bins_2D_25.png}
%
\includegraphics[width=0.35\textwidth]{cosmomc_kde/pl18_tanh_highz_test5_run1_vs_relike_tanh_highz_test9_run3_f0p10_taulo_prior_0p03_zre_prior_6p1_taulo_prior_0p0_tri.png}
\includegraphics[width=0.35\textwidth]{cosmomc_kde/pl18_tanh_highz_test5_run1_vs_relike_tanh_highz_test9_run3_f0p10_taulo_prior_0p03_zre_prior_6p1_taulo_prior_0p0_tri_smooth_scale_1D_2_num_bins_1D_20_smooth_scale_2D_2_num_bins_2D_25.png}
%
\label{fig:}
\caption{Left: Automated getdist smoothing; Right: hand tuned smoothing (slightly aggressive binning).
} 
\end{figure}

%\begin{figure}
%    \centering
%    \includegraphics{cosmomc_kde/pl18_tanh_highz_test5_run1_vs_relike_tanh_highz_test8_run9_f0p14_taulo_prior_0p03_zre_prior_6p1_taulo_prior_0p0393_tri.png}
%    \caption{$\taulo$ prior imposed at 0.0393, giving a straight cut in the 2D constraint, rather than the rounded zre = 6.1 prior.}
%    \label{fig:my_label}
%\end{figure}
